CLT item selection

### 2022-04-25 analysis/clt_item_selection.Rmd

		# Accept the new subset if it's an improvement, or if our
		# cooling coin came up heads.
		if(new_score > best_score | accept_decrease) {
			current_subset <- new_subset
			rejected <- 0
			if(new_score > best_score) {
				best_subset <- new_subset
				best_score <- new_score
				no_new_bests <- 0
			} else {
				no_new_bests <- no_new_bests + 1
			}
		# Quit if we've had too many rejections in a row.
		} else {
			rejected <- rejected + 1
			no_new_bests <- no_new_bests + 1
			if(rejected == break_thresh) {
				print(best_score)
				return(best_subset)
			}
		}
		# Start random resets to the current best subset if we haven't
		# found anything better in quite a while.
		if(no_new_bests > reset_thresh & rbernoulli(1, 1/100)) {
			current_subset <- best_subset
		}

>>>>

		# Accept the new subset if it's an improvement, or if our
		# cooling coin came up heads.
		if(new_score > best_score | accept_decrease) {
			current_subset <- new_subset
			rejected <- 0
			if(new_score > best_score) {
				best_subset <- new_subset
				best_score <- new_score
				no_new_bests <- 0
			} else {
				no_new_bests <- no_new_bests + 1
			}
		# Quit if we've had too many rejections in a row.
		} else {
			rejected <- rejected + 1
			no_new_bests <- no_new_bests + 1
			if(rejected == break_thresh) {
				#print(best_score)
			  ret <- tibble(best_subset = list(best_subset),
	              best_score = best_score)

				return(ret)
			}
		}
		# Start random resets to the current best subset if we haven't
		# found anything better in quite a while.
		if(no_new_bests > reset_thresh & rbernoulli(1, 1/100)) {
			current_subset <- best_subset
		}
